---
title: "HPV Microbiome Data Analysis"
author: "Myo Minn Oo"
output: word_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("script/hpv_microb.R")
```

## Comment

- there are `r sum(data.raw$HPV == "NA" | is.na(data.raw$HPV))` missing observations in HPV result. do we assume them as negative or remove them from further analysis? 



## Socio-demographic table 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
t1  
```

## HIV related table

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
t2
```

## Sexual behaviors and hygiene practices

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
t3
```

## HPV genotype distribution in HPV positive men stratified by HIV status

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
t4
```

```{r figs, echo=FALSE, fig.width=10,fig.height=10,fig.cap="\\label{fig:figs}HPV genotype distribution across different characteristics"}

fig1
```

## Association between risk factors and HPV infection using multivariable logistic regression 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
t5
```

